Dealing with Consumer Uncertainty: Online Consumer Reviews and What makes them helpful?

### 2022-11-08 Paper.Rmd
end of the third draft

theme_set(theme_bw(base_size = 12))

@@

Online shopping has becoming more and more prevalent in average consumer's daily life. Electronic shopping brought many advantages both for sellers and buyers. One of the positive perks is Online Consumer Reviews (OCR). Online Consumer Reviews come in the form of electronic word-of-mouth [@dellarocas2003] and can be defined as "*peer-generated product evaluations posted on company or third party websites*" [@mudambi2010]. OCR were found to have an effect on product sales as well as consumer decision making process. [@duan2008; @lee2011; @dellarocas2007].

@@

However, the increased rate of electronic commerce activity also created an abundance of product reviews on the internet. The vast amount of product reviews might increase the information overload on the customer [@sun2019; @fan2021]. Unfortunately, this information overload can make the search process even costlier because it is really time consuming to evaluate thousands of consumer reviews. Besides, not all reviews have the same informativeness level [@pan2011]. Therefore, answering the question of "what makes a helpful review?" is very important because reading more and more reviews without getting useful information can only increase the search costs. On top of this, the overload of useless information might impair the decision making ability of the potential buyer. To make the understanding of a "helpful review" more clear it can be strictly defined as "*a peer-generated product evaluation that facilitates the consumer's purchase decision process*" [@mudambi2010].

Having a good understanding of how consumers handle information and how their behaviors change with respect to information they are exposed to might even unearth newer tools to increase the social welfare because it would lead to a decreased level of information asymmetry between consumers and producers. The decreased information asymmetry might produce two benefits. First, consumers can learn to evaluate the quality of the products before purchase much more efficiently. This leaves less room for any dis-utility that can arise from purchasing a sub-par quality product. The second, the increased knowledge of the consumers towards certain products may even facilitate competition among firms. This competition may lead increased quality of the products as well as decreased prices in a given market. This is why understanding the determinants of a helpful review is important because it might reveal new insights on consumer behavior and these new insights could be used in favor of both consumers are producers.

@@

This study uses secondary data. The reviews were collected from two websites. Namely, IMDB and BestBuy. The data was scrapped with Selenium Webdriver for Python [@python3]. Over 400,000 reviews and their meta data were gathered initially. After the data transformation process the final sample size was over 23,000. Then this data was subjected to empirical tests. It was found out that consumers usually find extreme reviews more helpful than neutral ones. Furthermore, consumers prefer longer reviews when reviews are rated negatively. On the contrast, positive reviews with fewer words were deemed more helpful by readers on the average. In addition, the sentiment of a review has also a significant effect on the helpfulness of a review. These effects were further moderated by product types, namely, Search and Experience goods.

@@

Many different types of research methodologies were employed in the literature of the Review Helpfulness. To my knowledge the most common empirical analysis method that was used in the literature was Tobit Regression because of the limited and censored nature of the Reviews Helpfulness [@mudambi2010; @korfiatis2012; @huang2015; @choi2020; @ren2019; @chua2014]. Some of these studies also shared Ordinary Least Squares results alongside with the Tobit Regression results for the purpose of benchmarking [@mudambi2010; @kuan2015; @choi2020]. Ordinary Least Squares were also used as a main empirical methodology in some papers [@liu2014; @ghose2006; @lee2016]. Furthermore, Ordinary Least Squares was employed in a hierarchical manner as well [@baek2012]. Some other studies employed Multi-Level Regression model in order to deal with the potential selection bias which is present in the data [@ghose2011; @wu2021; @kuan2015]. In a rare case Ordinal Logistic Regression was one of the methods that was used to explain the determinants of the review helpfulness [@cao2011]. Predictive methods such as Neural Networks were used to understand the components of a helpful review as well [@lee2014]. One paper attacked the problem of the review helpfulness with three methods, namely, Partial Least Squares - Structural Equation Modelling, ANOVA Analysis and Artificial Neural Networks [@eslami2018].

@@

@nelson1970 also states that consumers can use other consumers' experiences in their search processes. The information about a certain good is usually acquired in the form of "word-of-mouth" in this kind of search process. This type of search is viable when getting the information about a certain product is much more costly by "experience" compared to by "search". For instance buying a laptop and trying to figure out if it is the best laptop for a certain task may even require buying additional laptops because of the need for comparison. This is the way of "experiencing" the good and this would be very costly. On the other hand, the potential buyer may want to hear from people who do the similar tasks with their laptops and try to sort out the best possible laptop model for her own task. This way she gets information about the product without having to "experience" it and this approach is way cheaper.

@@

```{r Search-Length, fig.height=6, fig.cap="The Distribution(A) and the Scatter Plot(C) of Review Length for Search Goods and respective logarithmic transformations (B), (D)"}
p1 <- search_goods %>% 
  ggplot(aes(Word_Count))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  geom_vline(aes(xintercept = mean(Word_Count)), size = 1, alpha = 0.6)+
  annotate(geom = "label", x = mean(search_goods$Word_Count), y = Inf, 
           label = paste("Mean:", round(mean(search_goods$Word_Count), digits = 0)),
           vjust = 1, hjust = 0, size = 4.5)+
  scale_x_continuous(n.breaks = 8)+
  labs(y = "Count", x = "Number of the Words")

@@

p2 <- search_goods %>% 
  ggplot(aes(Word_Count, Helpfulness))+
  geom_point(alpha = 0.1)+
  geom_smooth(color = "steelblue", size = 1.7)+
  scale_x_continuous(n.breaks = 8)+
  labs(x = "Number of the Words")

@@

```{r Search-Freshness, fig.height=6, fig.cap="The Distribution(A) and the Scatter Plot(C) of Review Freshness for Search Goods and respective logarithmic transformations (B), (D)"}
p1 <- search_goods %>% 
  ggplot(aes(Freshness))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  geom_vline(aes(xintercept = mean(Freshness)), size = 1, alpha = 0.6)+
  annotate(geom = "label", x = mean(search_goods$Freshness), y = Inf, 
           label = paste("Mean:", round(mean(search_goods$Freshness), digits = 0)),
           vjust = 1, hjust = 0, size = 4.5)+
  scale_x_continuous(n.breaks = 7)+
  labs(y = "Count", x = "Freshness of Review")

p1_log <- search_goods %>% 
  ggplot(aes(Freshness + 1))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 10)+
  geom_vline(aes(xintercept = mean(Freshness)), size = 1, alpha = 0.6)+
  annotate(geom = "label", x = mean(search_goods$Freshness), y = Inf, 
           label = paste("Mean:", round(mean(search_goods$Freshness), digits = 0)),
           vjust = 1, hjust = 0, size = 4.5)+
  scale_x_log10(n.break = 7)+
  labs(y = "Count", x = "log10(Freshness of Review + 1)")

p2 <- search_goods %>% 
  ggplot(aes(Freshness, Helpfulness))+
  geom_point(alpha = 0.1)+
  geom_smooth(color = "steelblue", size = 1.7)+
  scale_x_continuous(n.breaks = 7)+
  labs(x = "Freshness of Review")

p2_log <- search_goods %>% 
  ggplot(aes(Freshness + 1, Helpfulness))+
  geom_point(alpha = 0.1)+
  geom_smooth(color = "steelblue", size = 1.7)+
  scale_x_log10(n.breaks = 7)+
  labs(x = "log10(Freshness of Review + 1)")

@@

A number of reasons could be speculated about why the Hypothesis 5 and Hypothesis 6 did not hold for experience goods. The expectation was observing a negative significant coefficient for proportion of positive words and a positive significant coefficient for proportion of negative words. At the very least it can be said that the existence of positive words in a movie review does not offer a diagnostic value according to regression results. Thus, it is hard to say there is a strong deviation from Hypothesis 6. On the contrast, Hypothesis 5 for experience goods was not supported at all.

One reason of this might be that the NRC Word-Emotion Association Lexicon which was used to mine the negative words in the reviews was not suitable for the movie reviews. For instance, the word "*cage"* is a negative word in the lexicon and "*marvel*" is a positive word. One or more movies in the sample include movies where "Nicholas *Cage*" had the starring role. There are also "*Marvel* Cinematic Universe" movies present in the data. Cases like these may create noise for the variable and the model because aforementioned words were used frequently and outside of the context of the lexicon. To test this problem words such as "*cage, john, climax, force, king, mad, fury, hardy, margin, harry, marvel, stark, iron, vulture, green, goblin, bale*" were filtered out of the lexicon for both good types. Neither coefficient signs nor coefficient significances were changed. However, it should be pointed out that the coefficient of negative words for experience goods was weakened slightly. Further filtering was not pursued because of potential dangers of hypothesis fishing. (The results in Tables \@ref(tab:Reg-Results-Tobit) and \@ref(tab:Reg-Results-OLS) are the results with the filter.)

Another reason may arise from the subjective nature of the experience attributes of the movies. Negative words, in the context of electronics, may have narrower range of meanings because what they usually try to convey directly relates the to quality of the good itself. The quality of the good is easily accessible because of the fact that electronics have dominant search attributes. Thus, negative words probably translates as potential monetary risks rather than affecting emotions. A risk might be exemplified as purchasing a sub-par performing laptop with a given budget, in other words getting sub-optimal utility. Furthermore, electronics are usually bought to be used for a comparatively long period of time. A smartphone or a television can serve its owner for years so negative cues which relate to below average durability are very important. Buying a sub-durable product for a given budget can only increase the chances that the consumer will have to buy the same type of product prematurely in the future. On the other hand, the monetary risks associated with a bad movie are relatively lower. Consumers can go to cinema, buy a DVD, rent the movie on YouTube or access the movie as a part of their subscription plan on platforms such as Netflix. Subscription or ticket fees are not the only cost for the consumer. In order to consume the product the consumer must spend the time that is equal to the duration of the movie. Of course, the consumer can stop watching the movie anytime if it is too unbearable for her so she does not waste any more time. Because of these reasons the money spent on a movie might be irrelevant to an average consumer since accessing a movie is relatively cheaper than owning an electronic device. Therefore, negative words in a movie review may not alert the consumer for potential monetary losses. Instead, negative words could render a review in question unpleasant because emotions are priority in the case of consumption of movies.

-   read the paragraph below again. my brain is fucked.

There are still points to be made about the results of the movies. In the Section \@ref(search-and-experience-goods-classification) it was mentioned that consumers choose from two different strategies when they want to acquire information about a particular product. They might choose to experience the good or they can undertake search. It was pointed out by @nelson1970 that word-of-mouth type of information is viable when it is much more costlier to "experience" the good than undertaking a search process. It is probable that, in the case of movies, watching the movie (experiencing it) isn't that much costlier or maybe less costlier than gathering information about that particular movie and then making a decision on watching it. Thus, "search" might not be justifiable for movies. This might explain the unexpected results. Especially for the effect of the Review Length.

@@

Secondly, as pointed out in Section \@ref(literature-review), there were many different research designs present in the literature. Let alone different methodologies, even the utilizations of similar variables were contrasting. For instance, review extremity was employed in three different ways by researchers. This study and some others use the review ratings as it is. Another group of studies took the differences of review ratings from the mean rating of a given product. The resulting variable is usually called Review Inconsistency. The last group of researchers utilized a dummy variable for neutral reviews (3 out of 5) and extreme reviews (1,2,4,5 out of 5). In some studies these dummy variables were extended to negative and positive extreme dummies as well. The differences is not limited to Review Rating. The usages the dependent variable, Perceived Helpfulness, diverged as well. In some circumstances only absolute Helpful votes were used along with Negative Binomial Regression. Furthermore, some studies converted the percentage of the helpfulness into a binary problem where reviews with over 50% helpfulness score was considered as a helpful review. As a last example to different applications, scale transformations (logarithmic transformation, etc.) were applied liberally as well. All in all, it is clear that there is no standard approach in the literature which might be the reason why there are many conflicting results.

Potential omitted variables such as consumers' buying motivation or their trust towards strangers may also explain the conflicting or unexpected results as pointed out by @zhu2021. A person who is more agreeable will high likely find many more reviews helpful on the average. Additionally, buying motivation might play an important role in explaining the review helpfulness. Above, it was speculated that some consumers might have tendency towards certain brands or products. Favored brands might not be the only factor that affects the consumer motivation. For instance, a consumer with limited amount of budget may find positive reviews of products that have suitable prices helpful. Thus the product price relative to the consumer's budget can also be used as an indicator.

@@

Goods with very strong search or experience attributes were chosen in order to compare the information gathering process in the clearest way possible. The results proves the fact that information gathering is easier for search goods than experience goods. This means that consumers face less uncertainty against search goods. The results are only generalizable to laptops, phones, televisions and movies since different goods have different mix of search and experience attributes.

@@

1.  Reviewers should only write a review when their opinions of a given product is rather extreme.
2.  Reviewers should share all the information and the experience they accumulated about the product without making it too long because it was observed that helpfulness shows diminishing returns to additional words. The review should be clear and to the point.
3.  Reviewers should not refrain from using negative words as long as it objectively identifies something wrong or lacking with the given product.
4.  When reviewers are reviewing a product which they are extremely unhappy about they should give more details and elaborate, on the opposite, when they are content they should write relatively shorter reviews.
5.  Since recent reviews were found to be more helpful on the average, sharing updated information, i.e, writing new reviews is important and encouraged.

@@

There are some implications for the future studies. Firstly, aside from lexicon based sentiment analysis it is also possible to utilize deep learning methods to mine opinions from a text. One advantage of deep learning method over a lexicon is its versatility. A negative word can change from one context to another and training a deep learning method is more robust to this type of contextual changes whereas with lexicon based methods a negative word is a negative word no matter the context is. Next, future studies should consider collecting data from different regions and cultures. There might be some differences on how consumers process and react to the information in order to deal with uncertainty. Additionally, researchers can dig deeper into search and experience goods paradigm. It is well established in the literature that product type affects the information gathering process. However, there might be differences within product types depending on their search and experience attributes. An objective way to identify and index experience and search attributes may also shed some light to the conflicting results in the literature. Lastly, since Online Consumer Reviews data is ever growing more researchers should incorporate Exploratory Data Analysis into their works. Reviews and how helpful these reviews are perceived by potential buyers is relatively a new topic. In addition, new ways to analyze the text data are being developed so Online Consumer Reviews offer a great potential for new discoveries from the data for different domains. This increases the value of the Exploratory Data Analysis as well.

>>>>

theme_set(theme_bw(base_size = 12))
theme_update(axis.title = element_text(size = 13),
             axis.text = element_text(size = 12))

@@

Online shopping has becoming more and more prevalent in average consumer's daily life. Electronic shopping brought many advantages to both sellers and buyers. One of the positive perks is Online Consumer Reviews (OCR). Online Consumer Reviews come in the form of electronic word-of-mouth [@dellarocas2003] and can be defined as "*peer-generated product evaluations posted on company or third party websites*" [@mudambi2010]. OCR were found to have an effect on product sales as well as consumer decision making process. [@duan2008; @lee2011; @dellarocas2007].

@@

However, the increased rate of electronic commerce activity also created an abundance of product reviews on the internet. The vast amount of product reviews might increase the information overload on the customer [@sun2019; @fan2021]. Unfortunately, this information overload can make the search process even costlier because it is really time consuming to evaluate thousands of consumer reviews. Besides, not all reviews have the same informativeness level [@pan2011]. Therefore, answering the question of "what makes a helpful review?" is very important because reading more and more reviews without getting useful information can only increase the search costs. On top of this, the overload of useless information might impair the decision making ability of the potential buyer, leading to a sub-optimal choice. To make the understanding of a "helpful review" more clear it can be strictly defined as "*a peer-generated product evaluation that facilitates the consumer's purchase decision process*" [@mudambi2010].

Having a good understanding of how consumers handle information and how their behaviors change with respect to information they are exposed to might even unearth newer tools to increase the social welfare because it would lead to a decreased level of information asymmetry between consumers and producers. The decreased information asymmetry might produce two benefits. First, consumers can learn to evaluate the quality of the products before purchase much more efficiently. This leaves less room for any dis-utility that can arise from purchasing a sub-par quality product. The second, the increased knowledge of the consumers towards certain products may even facilitate competition among firms. This competition may lead increased quality of the products as well as decreased prices in a given market. This is why understanding the determinants of a helpful review is important because it might reveal new insights on consumer behavior and these new insights could be used in favor of both consumers and producers.

@@

This study uses secondary data. The reviews were collected from two websites. Namely, IMDB and BestBuy. The data was scrapped with Selenium Webdriver for Python [@python3]. Over 400,000 reviews and their meta data were gathered initially. After the data transformation process the final sample size was over 23,000. Then this data was subjected to empirical tests. It was found out that consumers usually find extreme reviews more helpful than neutral ones. Furthermore, consumers prefer longer reviews when reviews are rated negatively. On the contrast, positive reviews with fewer words were deemed more helpful by readers on the average. In addition, the sentiment of a review also has a significant effect on the helpfulness of a review. These effects were further moderated by product types, particularly, Search and Experience goods.

@@

Many different types of research methodologies were employed in the literature of the Review Helpfulness. To my knowledge the most common empirical analysis method that was used in the literature was Tobit Regression because of the limited and censored nature of the Reviews Helpfulness [@mudambi2010; @korfiatis2012; @huang2015; @choi2020; @ren2019; @chua2014]. Some of these studies also shared Ordinary Least Squares results alongside with the Tobit Regression results for the purpose of benchmarking [@mudambi2010; @kuan2015; @choi2020]. Ordinary Least Squares were also used as a main empirical methodology in some papers [@liu2014; @ghose2006; @lee2016]. Furthermore, Ordinary Least Squares was employed in a hierarchical manner as well [@baek2012]. Some other studies employed Multi-Level Regression model in order to deal with the potential selection bias which is present in the data [@ghose2011; @wu2021; @kuan2015]. In a rare case Ordinal Logistic Regression was one of the methods that was used to explain the determinants of the review helpfulness [@cao2011]. Predictive methods such as Neural Networks were used to understand the components of a helpful review as well [@lee2014]. One paper attacked the problem of the review helpfulness with three methods, specifically, Partial Least Squares - Structural Equation Modelling, ANOVA Analysis and Artificial Neural Networks [@eslami2018].

@@

@nelson1970 also states that consumers can use other consumers' experiences in their search processes. The information about a certain good is usually acquired in the form of "word-of-mouth" in this kind of search process. This type of search is viable when getting the information about a certain product is much more costly by "experience" compared to by "search", i.e., sampling the product is very costly. For instance buying a laptop and trying to figure out if it is the best laptop for a certain task may even require buying additional laptops because of the need for comparison. This is the way of "experiencing" the good and this would be very costly. On the other hand, the potential buyer may want to hear from people who do the similar tasks with their laptops and try to sort out the best possible laptop model for her own task. This way she gets information about the product without having to "experience" it and this approach is way cheaper.

@@

```{r Search-Length, fig.height=6, fig.cap="The Distribution(A) and the Scatter Plot(C) of Review Length for Search Goods and respective logarithmic transformations (B), (D)"}
p1 <- search_goods %>% 
  ggplot(aes(Word_Count))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  geom_vline(aes(xintercept = mean(Word_Count)), size = 1, alpha = 0.6)+
  annotate(geom = "label", x = mean(search_goods$Word_Count), y = Inf, 
           label = paste("Mean:", round(mean(search_goods$Word_Count), digits = 0)),
           vjust = 1, hjust = 0, size = 4.5)+
  scale_x_continuous(n.breaks = 7)+
  labs(y = "Count", x = "Number of the Words")

@@

p2 <- search_goods %>% 
  ggplot(aes(Word_Count, Helpfulness))+
  geom_point(alpha = 0.1)+
  geom_smooth(color = "steelblue", size = 1.7)+
  scale_x_continuous(n.breaks = 7)+
  labs(x = "Number of the Words")

@@

```{r Search-Freshness, fig.height=6, fig.cap="The Distribution(A) and the Scatter Plot(C) of Review Freshness for Search Goods and respective logarithmic transformations (B), (D)"}
p1 <- search_goods %>% 
  ggplot(aes(Freshness))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  geom_vline(aes(xintercept = mean(Freshness)), size = 1, alpha = 0.6)+
  annotate(geom = "label", x = mean(search_goods$Freshness), y = Inf, 
           label = paste("Mean:", round(mean(search_goods$Freshness), digits = 0)),
           vjust = 1, hjust = 0, size = 4.5)+
  scale_x_continuous(n.breaks = 6)+
  labs(y = "Count", x = "Freshness of Review")

p1_log <- search_goods %>% 
  ggplot(aes(Freshness + 1))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 10)+
  geom_vline(aes(xintercept = mean(Freshness)), size = 1, alpha = 0.6)+
  annotate(geom = "label", x = mean(search_goods$Freshness), y = Inf, 
           label = paste("Mean:", round(mean(search_goods$Freshness), digits = 0)),
           vjust = 1, hjust = 0, size = 4.5)+
  scale_x_log10(n.break = 6)+
  labs(y = "Count", x = "log10(Freshness of Review + 1)")

p2 <- search_goods %>% 
  ggplot(aes(Freshness, Helpfulness))+
  geom_point(alpha = 0.1)+
  geom_smooth(color = "steelblue", size = 1.7)+
  scale_x_continuous(n.breaks = 6)+
  labs(x = "Freshness of Review")

p2_log <- search_goods %>% 
  ggplot(aes(Freshness + 1, Helpfulness))+
  geom_point(alpha = 0.1)+
  geom_smooth(color = "steelblue", size = 1.7)+
  scale_x_log10(n.breaks = 6)+
  labs(x = "log10(Freshness of Review + 1)")

@@

A number of reasons could be speculated about why the Hypothesis 5 and Hypothesis 6 did not hold for experience goods. The expectation was observing a negative significant coefficient for proportion of positive words and a positive significant coefficient for proportion of negative words. At the very least it can be said that the existence of positive words in a movie review does not offer a significant information value according to regression results. Thus, it is hard to say there is a strong deviation from Hypothesis 6. On the contrast, Hypothesis 5 for experience goods was not supported at all.

One reason of this might be that the NRC Word-Emotion Association Lexicon which was used to mine the negative words in the reviews was not suitable for the movie reviews. For instance, the word "*cage"* is a negative word in the lexicon and "*marvel*" is a positive word. One or more movies in the sample include movies where "Nicholas *Cage*" had the starring role. There are also "*Marvel* Cinematic Universe" movies present in the data. Cases like these may create noise for the variable and the model because aforementioned words were used frequently and outside of the context of the lexicon. To test this problem, negative and positive words such as "*cage, john, climax, force, king, mad, fury, hardy, margin, harry, marvel, stark, iron, vulture, green, goblin, bale*" were filtered out of the lexicon for both good types. Neither coefficient signs nor coefficient significances were changed. However, it should be pointed out that the magnitude of the coefficient of negative words for experience goods was weakened slightly. Further filtering was not pursued because of potential dangers of hypothesis fishing. (The results in Tables \@ref(tab:Reg-Results-Tobit) and \@ref(tab:Reg-Results-OLS) are the results with the filter.)

Another reason may arise from the subjective nature of the experience attributes of the movies. Negative words, in the context of electronics, may have a narrower range of meanings because what they usually try to convey directly relates the to quality of the good itself. The quality of the good is easily accessible because of the fact that electronics have dominant search attributes. Thus, negative words probably translates as potential monetary risks rather than affecting emotions. A risk might be exemplified as purchasing a sub-par performing laptop with a given budget, in other words getting sub-optimal utility. Furthermore, electronics are usually bought to be used for a comparatively long period of time. A smartphone or a television can serve its owner for years so negative cues which relate to below average durability are very important. Buying a sub-durable product for a given budget can only increase the chances that the consumer will have to buy the same type of product prematurely in the future. On the other hand, the monetary risks associated with a bad movie are relatively lower. Consumers can go to cinema, buy a DVD, rent the movie on YouTube or access the movie as a part of their subscription plan on platforms such as Netflix. Subscription or ticket fees are not the only cost for the consumer. In order to consume the product the consumer must spend the time that is equal to the duration of the movie. Of course, the consumer can stop watching the movie anytime if it is too unbearable for her so she does not waste any more time. Because of these reasons the money spent on a movie might be irrelevant to an average consumer since accessing a movie is relatively cheaper than owning an electronic device. Therefore, negative words in a movie review may not alert the consumer for potential monetary losses. Instead, negative words could render a review in question unpleasant because emotions are priority in the case of consumption of movies.

There are still points to be made about the results of the movies. In the Section \@ref(search-and-experience-goods-classification) it was mentioned that consumers choose from two different strategies when they want to acquire information about a particular product. They might choose to experience the good or they can undertake search in order to collect information. It was pointed out by @nelson1970 that word-of-mouth type of information is viable when it is much more costlier to "experience" the good than undertaking a search process. It is probable that, in the case of movies, watching the movie (experiencing it) isn't that much costlier or maybe less costlier than gathering information about that particular movie and then making a decision on watching it. Thus, "search" might not be very justifiable for movies. This might explain why electronic word-of-mouth (Review Length) showed rather weaker and erratic (positive for lower ratings, negative for higher ratings) results.

@@

Secondly, as pointed out in Section \@ref(literature-review), there were many different research designs present in the literature. Let alone different methodologies, even the utilizations of similar variables were contrasting. For instance, review extremity was employed in three different ways by researchers. This study and some others use the review ratings as it is. Another group of studies took the differences of review ratings from the mean rating of a given product. The resulting variable is usually called Review Inconsistency. The last group of researchers utilized a dummy variable for neutral reviews (3 out of 5) and extreme reviews (1,2,4,5 out of 5). In some studies these dummy variables were extended to negative and positive extreme dummies as well. The differences are not limited to Review Rating. The usages the dependent variable, Perceived Helpfulness, diverged as well. In some circumstances only absolute Helpful votes were used along with Negative Binomial Regression. Furthermore, some studies converted the percentage of the helpfulness into a binary problem where reviews with over 50% helpfulness score was considered as a helpful review. As a last example to different applications, scale transformations (logarithmic transformation, etc.) were applied liberally as well. All in all, it is clear that there is no standard approach in the literature which might be the reason why there are many conflicting results.

Potential omitted variables such as consumer's buying motivation or his/her trust towards strangers may also explain the conflicting or unexpected results as pointed out by @zhu2021. A person who is more agreeable will high likely find many more reviews helpful on the average. Additionally, buying motivation might play an important role in explaining the review helpfulness. Above, it was speculated that some consumers might have tendency towards certain brands or products. Favored brands might not be the only factor that affects the consumer motivation. For instance, a consumer with limited amount of budget may find positive reviews of products that have suitable prices helpful. Thus the product price relative to the consumer's budget can also be used as an indicator.

@@

Goods with very strong search or experience attributes were chosen in order to compare the information gathering process in the clearest way possible. The results prove the fact that information gathering is easier for search goods than experience goods. This means that consumers face less uncertainty against search goods. The results are only generalizable to laptops, phones, televisions and movies since different goods have different mix of search and experience attributes.

@@

1.  Reviewers should only write a review when their opinions of a given product is rather extreme.
2.  Reviewers should share all the information and the experience they accumulated about the product without making it too long because it was observed that helpfulness shows diminishing returns to additional words. The review should be clear and to the point.
3.  Reviewers should not refrain from using negative words as long as it objectively identifies something wrong or lacking with the product which is being reviewed.
4.  When reviewers are reviewing a product which they are extremely unhappy about they should give more details and elaborate, on the opposite, when they are content they should write relatively shorter reviews.
5.  Since recent reviews were found to be more helpful on the average, sharing updated information, i.e, writing new reviews is important and encouraged.

@@

There are some implications for the future studies. Firstly, aside from lexicon based sentiment analysis it is also possible to utilize deep learning methods to mine opinions from a text. One advantage of deep learning method over a lexicon is its versatility. A negative word can change from one context to another and training a deep learning method is more robust to this type of contextual changes whereas with lexicon based methods a negative word is a negative word no matter the context is. Next, future studies should consider collecting data from different regions and cultures. There might be some differences on how consumers process and react to the information in order to deal with uncertainty. Additionally, researchers can dig deeper into search and experience goods paradigm. It is well established in the literature that product type affects the information gathering process. However, there might be differences within product types depending on their search and experience attributes. An objective way to identify and index experience and search attributes may also shed some light to the conflicting results in the literature. Lastly, since Online Consumer Reviews data is ever growing more researchers should incorporate Exploratory Data Analysis into their works. Reviews and how helpful these reviews are perceived by potential buyers is relatively a new topic. In addition, new ways to analyze text data are being developed since the area of Natural Language Processing is quite hot so Online Consumer Reviews offer a great potential for new discoveries from the data for different domains. This increases the value of the Exploratory Data Analysis as well.
